3.5 Decision Tree
3.5.1 approches
To solve the problem, we use the decision trees method.[Y1-2]. Decision tree (DT) induction [Y3] is a supervised classification and prediction technique with a long history going ba4ck over three decades [Y4]. A decision tree is a tree where each node shows a feature (attribute), each link (branch) shows a decision (rule) and each leaf shows an outcome (categorical or continues value)[Y5]Decision Tree algorithm as follows, Firstly, Set the dataset's best feature as the root of the tree. Secondly, Dataset is split into test and train sets. Subsets should be made in such a way that each subset contains information with the feature attribute like that. Then, On each subset, the steps above are repeated until we get leaves in the tree.[Y6]





3.5.3 parameter setting
We tried different combinations of the parameters ,the given following is the best choice. For parameters, use criterion, The function to measure the quality of a split. Supported criteria are “gini” for the Gini impurity and “log\_loss” and “entropy” both for the Shannon information gain.





References
[Y1] A. Albu, From logical inference to decision trees in medical diagnosis, Proceedings of 2017 EHealth and Bioengineering Conference (2017) 65-68. doi: 10.1109/EHB.2017.7995362 
[Y2] M.D.A. Praveena, J. S. Krupa, S. SaiPreethi, Statistical Analysis Of Medical Appointments Using Decision Tree, Conference on Science Technology Engineering and Mathematics (2019) 59-64. doi: 10.1109/ICONSTEM.2019.8918766
[Y3] Lior, R., Maimon, O.: Data mining with decision trees: theory and applications, vol. 81. World Scientific, 2 edn. (2014)
[Y4] Quinlan, J.R.: Induction of decision trees. Machine learning 1(1), 81–106 (1986)
[Y5] Jadhav SD, Channe HP. Efficient recommendation system using decision tree classifier and collaborative filtering. Int. Res. J. Eng. Technol. 2016;3:2113-8.
[Y6] Kavitha M, Gnaneswar G, Dinesh R, et al. Heart disease prediction using hybrid machine learning model[C]//2021 6th International Conference on Inventive Computation Technologies (ICICT). IEEE, 2021: 1329-1333.
[Y7] Chandrasekar P, Qian K, Shahriar H, et al. Improving the prediction accuracy of decision tree mining with data preprocessing[C]//2017 IEEE 41st Annual Computer Software and Applications Conference (COMPSAC). IEEE, 2017, 2: 481-484.
